Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-07-25 ch04-lrmhinf/lrmhinf.tex
Small changes in control intermezzo

\section{Intermezzo: Basics of Robust Control}
\label{sec:lrmhinf:robust-control-basics}
When designing a feedback controller $\Controller$ (as in \figref{fig:lrmhinf:tpc:nominal}), the goal is to design $\Controller$ such that the output $y$ of a plant $\true{\Plant}$ follows the command signal $r_2$ with some additional constraints on the performance of the whole closed-loop system (e.g. limited overshoot, short response times, good disturbance suppression, limited controller effort, \ldots).
This obviously requires knowledge of the actual plant $\true{\Plant}$ that is to be controlled.
Such knowledge can be obtained by means of modeling, be it first-principles modeling or system identification or a combination of modeling approaches, which provides an approximate model $\estimated{\Plant}$.

@@

In robust control~\citep{Zhou1996,Skogestad2005}, the design is carried out while taking uncertainties into account.
This is typically done by considering that the actual plant $\true{\Plant} \in \ModelSet[]$.
Hence, the problem is then to construct the model set $\ModelSet[]$ as illustrated in \figref{fig:lrmhinf:modelset}.
The design process thus guarantees performance and stability for the whole set instead of for a single model.
However, these guarantees hinge on proper specification of $\ModelSet[]$ which is typically done by estimating a nominal model $\estimated{\Plant}$ and the model error $\Delta(\estimated{\Plant}, \true{\Plant})$.
A generic way to express the plant model set (see also \figref{fig:lrmhinf:modelset}) is
\begin{equation}
  \ModelSet[]_{\mathrm{generic}} 
  \isdef 
  \Set{ \Plant | \norm{\Delta(\estimated{\Plant}, \Plant)} \leq \gamma}
  \label{eq:lrmhinf:model-set:generic}
\end{equation}
where both the norm and the exact uncertainty description $\Delta(\estimated{\Plant}, \Plant)$, can be chosen by the control engineer.
An example of such a model set is easily imagined for additive uncertainty ($\Plant = \estimated{\Plant} + \Delta$) when a $\Hardy_{2}$ norm is used, in that case one obtains
\begin{equation}
  \ModelSet[]_{\mathrm{additive,2}} 
  = 
  \Set{ \Plant | \Bignorm[2]{ \ezbrace{\Plant - \estimated{\Plant}}{\Delta(\estimated{\Plant}, \Plant)}  } \leq \gamma}
  \equiv
  \Set{  \ezbrace{\estimated{\Plant}  + \Delta}{\Plant(\estimated{\Plant}, \Delta)}  | \norm[2]{\Delta} \leq \gamma}
  \text{,}
\end{equation}
which is a multidimensional ball with radius $\gamma$ centered around $\estimated{\Plant}$.
Note that in many cases, the uncertainty structure (additive, multiplicative, \ldots) can be converted to other representations~\citep{Douma2005}.

>>>>

\section{Intermezzo: Basics of Robust Control}
\label{sec:lrmhinf:robust-control-basics}
When designing a feedback controller $\Controller$ (as in \figref{fig:lrmhinf:tpc:nominal}), the goal is to design $\Controller$ such that the output $y$ of a plant $\true{\Plant}$ follows the command signal $r_2$ with some additional constraints on the performance of the whole closed-loop system (e.g. limited overshoot, short response times, good disturbance suppression, limited controller effort $u_c$, \ldots).
This obviously requires knowledge of the actual plant $\true{\Plant}$ that is to be controlled.
Such knowledge can be obtained by means of modeling, be it first-principles modeling or system identification or a combination of modeling approaches, which provides an approximate model $\estimated{\Plant}$.

@@

In robust control~\citep{Zhou1996,Skogestad2005}, the design is carried out while taking uncertainties into account.
This is typically done by considering that the actual plant $\true{\Plant} \in \ModelSet[]$.
Hence, the problem is then to construct the model set $\ModelSet[]$ as illustrated in \figref{fig:lrmhinf:modelset}.
The design process thus guarantees performance and stability for the whole set instead of for a single model.
However, these guarantees hinge on proper specification of $\ModelSet[]$ which is typically done by estimating a nominal model $\estimated{\Plant}$ and the model error $\Delta(\estimated{\Plant}, \true{\Plant})$.
A generic way to express the plant model set (see also \figref{fig:lrmhinf:modelset}) is
\begin{equation}
  \ModelSet[]_{\mathrm{generic}} 
  \isdef 
  \Set{ \Plant | \norm{\Delta(\estimated{\Plant}, \Plant)} \leq \gamma}
  \label{eq:lrmhinf:model-set:generic}
\end{equation}
where both the norm and the exact uncertainty description $\Delta(\estimated{\Plant}, \Plant)$, can be chosen by the control engineer.
An example of such a model set is easily imagined for additive uncertainty ($\Plant = \estimated{\Plant} + \Delta$) when a $2$-norm is used, in that case one obtains
\begin{equation}
  \ModelSet[]_{\mathrm{additive,2}} 
  = 
  \Set{ \Plant | \Bignorm[2]{ \ezbrace{\Plant - \estimated{\Plant}}{\Delta(\estimated{\Plant}, \Plant)}  } \leq \gamma}
  \equiv
  \Set{  \ezbrace{\estimated{\Plant}  + \Delta}{\Plant(\estimated{\Plant}, \Delta)}  | \norm[2]{\Delta} \leq \gamma}
  \text{,}
\end{equation}
which is a multidimensional ball with radius $\gamma$ centered around $\estimated{\Plant}$.
Note that in many cases, the uncertainty structure (additive, multiplicative, \ldots) can be converted to other representations~\citep{Douma2005}.
